### 2013-09-26 Tex/chapters/results.tex
fehlerkorrektur

    For evaluation the Monte Carlo simulation is run until the system
    is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
    and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
    per site \(E=\frac{1}{N} H\) are calculated and saved for every
    \(2\tau\) sweeps, where \(\tau\) denotes the \emph{autocorrelation time}
    (see also Sec.\ \ref{sssec:eqtime}). The used values for different system sizes
    are listed in Tab.\ \ref{tab:tauAndTeq} in numbers of sweeps. Note that
    the \(t_{eq}\) values are generously rounded up to be on the safe side
    and the \(\tau\) values are determined as the maximum \(\tau\) over all
    simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
    and rounded up to the next integer.
        \begin{tabular}{l r r r r r}
            \(L\)    & 16 &  32 &  64 & 128 & 256\\
            \(\tau\) &  3 &   5 &   7 &  12 &  16\\
            \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
        \caption[Autocorrelation Times $\tau$ and Equilibration Times
            $t_{eq}$ for Different System Sizes $L$]{
            Autocorrelation times $\tau$ and equilibration times
            $t_{eq}$ for different system sizes $L$. All values are generously
            rounded up and determined as the maximum over all \(\sigma\) and \(T\).
        \label{tab:tauAndTeq}
    For every observable \(O\) the expected value \(\avg{O}\) is determined
    as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
    or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
    calculated sweeps totals to
    \[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}.\]
    The expected values \(\avg{O}\) for \(100\) different random proximity
    graphs with the same disorder parameter \(\sigma\) are then averaged to
    \(\overline{\avg{O}}\). Note that the signs \(\overline{\avg{\cdot}}\)
    are omitted in the following for the sake of simplicity so
    it will be just called \(O\).\\
    Not only the seed to generate the new random
    realization of the proximity graph is changed, but also the seed for
    the random numbers used in the Monte Carlo simulation and during the
    generation of the random start configuration of the spins.\\
    The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrap resampling
    \cite{Bootstrap}.\\
    There are two kinds of errors in this simulations. On the one hand
    there are thermal fluctuations in the simulation of one graph realization and
    on the other hand there are fluctuations in the structure of the realizations.
    To account for both, first a resampling of the "timeline" of one
    realization is performed. From these resamples the expected values of
    the observables \(\avg\abs{m}, \chi\) and \(g\) are estimated for each
    realization. Those are then resampled and from the resampled values
    one bootstrap average \(\avg{O}b\) is calculated. This procedure is
    repeated until 20 different bootstrap averages are present. Their
    mean and standard deviation are the used as \(\overline{\avg{O}}\) and
    its standard error \(\Delta \overline{\avg{O}}\). A shematic figure of
    this is shown in Fig.\ \ref{fig:bootstrap}.
    % TODO
    For every determined value an
    error is calculated and given in the form \texttt{value(error of last digit)}.
    The errors of fit parameters are the asymptotic standard errors as calculated
    by gnuplot divded by root of the chi-squared per degree of freedom
    as stated in \cite{young2012everything}. Gnuplot\footnote{\url{http://gnuplot.info/}.} is an open
    source plotting program used for all plots and fits in this thesis.
    Also note that dotted lines in the plots are -- if not noted otherwise --
    cubic spline interpolations purely meant to be guides to the eye.

>>>>

    For evaluation the Monte Carlo simulation is run until the system
    is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
    and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
    per site \(E=\frac{1}{N} H\) are calculated and saved for every
    \(2\tau\) sweeps, where \(\tau\) denotes the \emph{autocorrelation time}
    (see also Sec.\ \ref{sssec:eqtime}). The used values for different system sizes
    are listed in Tab.\ \ref{tab:tauAndTeq} in numbers of sweeps. Note that
    the \(t_{eq}\) values are generously rounded up to be on the safe side
    and the \(\tau\) values are determined as the maximum \(\tau\) over all
    simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
    and rounded up to the next integer.
    \begin{table}[htbp]
        \center
        \begin{tabular}{l r r r r r}
            \toprule
            \(L\)    & 16 &  32 &  64 & 128 & 256\\
            \midrule
            \(\tau\) &  3 &   5 &   7 &  12 &  16\\
            \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
            \bottomrule
        \end{tabular}
        \caption[Autocorrelation Times $\tau$ and Equilibration Times
            $t_{eq}$ for Different System Sizes $L$]{
            Autocorrelation times $\tau$ and equilibration times
            $t_{eq}$ for different system sizes $L$. All values are generously
            rounded up and determined as the maximum over all \(\sigma\) and \(T\).
        }
        \label{tab:tauAndTeq}
    \end{table}\\
    For every observable \(O\) the expected value \(\avg{O}\) is determined
    as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
    or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
    calculated sweeps totals to
    \[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}.\]
    The expected values \(\avg{O}\) for \(100\) different random proximity
    graphs with the same disorder parameter \(\sigma\) are then averaged to
    \(\overline{\avg{O}}\). Note that the signs \(\overline{\avg{\cdot}}\)
    are omitted in the following for the sake of simplicity so
    it will be just called \(O\).\\
    Not only the seed to generate the new random
    realization of the proximity graph is changed, but also the seed for
    the random numbers used in the Monte Carlo simulation and during the
    generation of the random start configuration of the spins.\\
    The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrap resampling
    \cite{Bootstrap}.
    There are two kinds of errors in this simulations. On the one hand
    there are thermal fluctuations in the simulation of one graph realization and
    on the other hand there are fluctuations in the structure of the realizations.
    To account for both, first a resampling of the "timeline" of one
    realization is performed. From these resamples the expected values of
    the observables \(\avg{\abs{m}}, \chi\) and \(g\) are estimated for each
    realization. Those are then resampled and from the resampled values
    one bootstrap average \(\avg{O}_b\) is calculated. This procedure is
    repeated until 20 different bootstrap averages are present. Their
    mean and standard deviation are used as \(\overline{\avg{O}}\) and
    its standard error \(\Delta \overline{\avg{O}}\).
    For every determined value an
    error is calculated and given in the form \texttt{value(error of last digit)}.
    The errors of fit parameters are the asymptotic standard errors as calculated
    by gnuplot divded by root of the chi-squared per degree of freedom
    as stated in \cite{young2012everything}. Gnuplot\footnote{\url{http://gnuplot.info/}.} is an open
    source plotting program used for all plots and fits in this thesis.
    Also note that dotted lines in the plots are -- if not noted otherwise --
    cubic spline interpolations purely meant to be guides to the eye.
